Kepler and the Behemoth: Three Mini-Neptunes in a 40 Million Year Old Association

### 2022-09-06 papers/paper/ms.tex
update response (H-a, Li)

		\vspace{-0.35cm}
		\subfloat{
			\includegraphics[width=0.48\textwidth]{f6c.pdf}
		}
	\end{center}
	\vspace{-0.6cm}
	\caption{
    {\bf Lithium 6708\AA\ and H$\alpha$ equivalent widths for the
    objects of interest compared to young open clusters and field
    stars. } Positive equivalent width means absorption; negative
    equivalent width means emission.  
    {\it Top \& middle}:
    The field stars are KOIs from
    \citet{berger_identifying_2018}.  The ``40-50 Myr'' reference
    stars ({\it left}) are from IC\,2602 \replaced{\citep{randich_gaiaeso_2018}}{\citep{randich_2001}} and
    Tuc-Hor \citep{kraus_stellar_2014}.  The ``112 Myr'' stars
    are from the Pleiades
    \citep{soderblom_evolution_1993,jones_evolution_1996,bouvier_pleiades_lirot_2018}.
    The statistical uncertainties on
    the equivalent widths are shown, or else are
    smaller than the markers.
    {\it Bottom}:
    The H$\alpha$ comparison is against Tuc-Hor
    \citep[$\approx$$40$\,Myr;][]{kraus_stellar_2014}
    \label{fig:lithium}
	}
\end{figure}

@@

Our preferred explanation for Kepler-1643's meager lithium 
content is that the reference sample\added{s} of IC\,2602 and Tuc-Hor
stars may not fully explore all possible stellar rotation
periods and lithium equivalent widths at this age.
\added{This would be somewhat surprising since over a dozen
stars have already been analyzed in the relevant effective temperature range. However, considering}
the top panels of Figure~\ref{fig:lithium}, it is remarkable that in
50 million years, stars between $4500$\,K and $5200$\,K go from
having a tight lithium sequence to one with a dispersion
$\approx10\times$ greater.  The existence of the Li dispersion in
Pleiades-age K-dwarfs has been known for decades; it has also been
known that the stars with the largest lithium abundances are also the
most rapidly rotating
\citep{butler_pleiades_1987,soderblom_evolution_1993}.  More recent
analyses of this correlation have been reviewed by
\citet{bouvier_lithium-rotation_2020}.  The conclusion of that work
was that the origin of the rotation-lithium correlation likely lies
within pre-main-sequence stellar physics.  If so, one would expect the
IC\,2602 and Tuc-Hor K-dwarfs to show a larger intrinsic lithium
dispersion.  A recent analysis of the $\approx$40\,Myr
NGC~2547 by \citet{binks_2022} suggests that this may
be the case, though that study only had $\approx$10 stars in the relevant
effective temperature range.
\added{An alternative explanation could be that the overall metallicity of the cluster 
is different from Tuc-Hor and IC\,2602, but this seems unlikely given the near-solar
metallicities we have measured for the Kepler Objects of Interest.}
\replaced{This suggests}{Broadly, these considerations suggest} that
RSG-5 and Cep-Her could be
worthy objects for a \replaced{closer analysis of the lithium-rotation correlation}{spectroscopic analysis of lithium}
near the zero-age main sequence.

@@

Balmer line emission, particularly in H$\alpha$, is expected for
low-mass stars of this age.  \citet{kraus_stellar_2014} for instance, in their
survey of Tuc-Hor ($\approx$40\,Myr), observed that all
cluster members with spectral types $>$${\rm K4.5V}$ had H$\alpha$ in
emission.  Ths is consistent with our observations: KOI-7913 shows
H$\alpha$ in emission for both components, and in absorption
for all of our other Kepler objects (Figure~\ref{fig:koiyouthindicators}, lower panel).  The double-peaked nature of the
emission, though not always present, is also common for
active stars.  Proxima Centauri, for instance, has double-peaked
H$\alpha$ emission \citep{collins_calculations_2017}.  Given
that we have ruled out spectroscopic binarity, the most
likely
explanation is self-absorption: photons near the center of the line
see a greater optical depth from higher layers of the chromosphere,
while photons on the wings are too far from the
rest-wavelength to excite electrons and be re-absorbed in the upper
layers.  The exact details of when a star's atmosphere reaches the
conditions for such self-absorption require non-local thermal
equilibrium models of the chromosphere
\citep{short_chromospheric_1998,2005A&A...439.1137F}.

>>>>

		\vspace{-0.35cm}
		\subfloat{
			\includegraphics[width=0.48\textwidth]{f6c.pdf}
		}
	\end{center}
	\vspace{-0.6cm}
	\caption{
    {\bf Lithium 6708\AA\ and H$\alpha$ equivalent widths for the
    objects of interest compared to young open clusters and field
    stars. } Positive equivalent width means absorption; negative
    equivalent width means emission.  
    {\it Top \& middle}:
    The field stars are KOIs from
    \citet{berger_identifying_2018}.  The ``40-50 Myr'' reference
    stars ({\it left}) are from IC\,2602 \replaced{\citep{randich_gaiaeso_2018}}{\citep{randich_2001}} and
    Tuc-Hor \citep{kraus_stellar_2014}.  The ``112 Myr'' stars
    are from the Pleiades
    \citep{soderblom_evolution_1993,jones_evolution_1996,bouvier_pleiades_lirot_2018}.
    The statistical uncertainties on
    the equivalent widths are shown, or else are
    smaller than the markers.
    {\it Bottom}:
    The H$\alpha$ comparison is against Tuc-Hor
    \citep[$\approx$$40$\,Myr;][]{kraus_stellar_2014}\added{ and the Pleiades \citep{fang_2018}.}
    \label{fig:lithium}
	}
\end{figure}

@@

Our preferred explanation for Kepler-1643's meager lithium 
content is that the reference sample\added{s} of IC\,2602 and Tuc-Hor
stars may not fully explore all possible stellar rotation
periods and lithium equivalent widths at this age.
\added{This would be somewhat surprising since over a dozen stars have
already been analyzed in the relevant effective temperature range.
However, considering}
the top panels of Figure~\ref{fig:lithium}, it is \added{also} remarkable that in
50 million years, stars between $4500$\,K and $5200$\,K go from
having a tight lithium sequence to one with a dispersion
$\approx10\times$ greater.  The existence of the Li dispersion in
Pleiades-age K-dwarfs has been known for decades; it has also been
known that the stars with the largest lithium abundances are also the
most rapidly rotating
\citep{butler_pleiades_1987,soderblom_evolution_1993}.  More recent
analyses of this correlation have been reviewed by
\citet{bouvier_lithium-rotation_2020}.  The conclusion of that work
was that the origin of the rotation-lithium correlation likely lies
within pre-main-sequence stellar physics.  If so, one would expect the
IC\,2602 and Tuc-Hor K-dwarfs to show a larger intrinsic lithium
dispersion.  A recent analysis of the $\approx$40\,Myr
NGC~2547 by \citet{binks_2022} suggests that this may
be the case, though that study only had $\approx$10 stars in the relevant
effective temperature range.
\added{An alternative explanation could be that the overall metallicity of Cep-Her
is different from Tuc-Hor and IC\,2602, but this seems unlikely given the near-solar
metallicities we have measured for the Kepler Objects of Interest.}
\replaced{This suggests that RSG-5 and Cep-Her could be worthy objects for a
closer analysis of the lithium-rotation correlation near the zero-age
main sequence.}{Broadly, these considerations suggest that Cep-Her is
a worthy object for further spectroscopic analyses of lithium near the
zero-age main sequence.}

@@

Balmer line emission, particularly in H$\alpha$, is expected for
low-mass stars of this age.  \citet{kraus_stellar_2014} for instance, in their
survey of Tuc-Hor ($\approx$40\,Myr), observed that all
cluster members with spectral types $>$${\rm K4.5V}$ had H$\alpha$ in
emission.  This is consistent with our observations: KOI-7913 shows
H$\alpha$ in emission for both components, and in absorption
for all of our other Kepler objects (Figure~\ref{fig:koiyouthindicators}, lower panel).  The double-peaked nature of the
emission, though not always present, is also common for
active stars.  Proxima Centauri, for instance, has double-peaked
H$\alpha$ emission \citep{collins_calculations_2017}.  Given
that we have ruled out spectroscopic binarity, the most
likely
explanation is self-absorption: photons near the center of the line
see a greater optical depth from higher layers of the chromosphere,
while photons on the wings are too far from the
rest-wavelength to excite electrons and be re-absorbed in the upper
layers.  The exact details of when a star's atmosphere reaches the
conditions for such self-absorption require non-local thermal
equilibrium models of the chromosphere
\citep{short_chromospheric_1998,2005A&A...439.1137F}.
